Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-05 paper.tex
more on portability

       \section{Tool installation}

@@

             Containeri
            use of containers increase portability. none of the scientific 
            pipelines can be containerized and communicate with the scheduler 
            outside of the container
            big data frameworks can
    \chapter{Reproducibility}\label{reproducibility}
        Reproducibility is a critical component to all scientific workflows. 
        Without reproducibility, correctness of results could never be 
        determined \tristan{Link between two first sentences could be smoothened}. Reproducibility is defined as the ability to obtain similar 
        results by 
        recreating or executing the original workflow on the same or different
        infrastructure\note{cite Peng 2011}. It has been found that more than 70\% of
        scientific experiments are not reproducible \note{cite Mbaker}

>>>>

            Containers are lightweight solutions to isolating 
            environments. Although similar, containers and virtual machines 
            differ from each 
            other in that VMs virtualize the
            hardware by running an entirely different operating system, whereas
            containers virtualize the software by running on top of the host's
            kernel.

            Containerization greatly increases the portability of workflows. 
            They allows users to package their workflows and/or tools with all 
            their dependencies in a package that users can download and 
            execute. Moreover, these packages can be versioned permitting users 
            to select the preferred version of the container. Although there 
            exist many containerization technologies, the two most notable ones
            in scientific computing are Docker and Singularity. Docker and 
            Singularity are both platform independent meaning users can run
            containerizaed versions of their workflows ontop of an otherwise
            incompatible OS.

            Singularity is the current preferred solution for running 
            containers on HPC systems. It is an open-source project designed to
            meet the security, portability and reproducibility requirements of 
            the scientific community. The main difference between Docker and 
            Singularity is that users gain root permissions in a Docker 
            container, and thus obtain root access to the underlying host OS. 
            This is a serious security concern in HPC systems where many users
            share the same resources and therefore are given restricted access
            only. Singularity addresses this concern by disabling the user from
            acquiring elevated permissions within the container.

            Containers are widely used to isolate tool executions and eliminate
            the need to manually install dependencies in scientific workflows.
            Pipeline tools can be containerized. In neuroinformatics, 
            NeuroDocker, a command-line tool for creating Docker and 
            Singularity containers with specific versions of neuroimaging tools
            installed. Examples of 
            containerized applications include all of the BIDS Apps. 
            Additionally, entire workflows can also be containerized, as can be
            observed in fMRIPrep, a Nipype-based workflow for fMRI 
            Preprocessing.

       \section{Tool sharing}\label{sharing}

@@

    \chapter{Reproducibility}\label{reproducibility}
        Reproducibility is a critical component to all scientific workflows. 
        Without reproducibility, correctness of results could never be 
        determined \tristan{Link between two first sentences could be smoothened}. Reproducibility is defined as the ability to obtain similar 
        results by 
        recreating or executing the original workflow on the same or different
        infrastructure\note{cite Peng 2011}. It has been found that more than 70\% of
        scientific experiments are not reproducible \note{cite Mbaker}
